Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-30 paper.tex
Drop separate vcztools methods section
Closes #256

@@

\subsection{vcztools}
Vcztools is available for download on the Python package index, and
supports all major platforms [TODO do we support Windows??],
and is written in a combination of Python and C.
We use
the Zarr-Python package~\citep{zarrpython} for all Zarr operations.
The mini-language in the \texttt{query} command is parsed using
PyParsing [TODO cite].
[Add a note here on why it was easier to to write a Python application
from scratch than to update bcftools.]

As a general principle, data is only retrieved from the Zarr store
when it is required to fulfil a particular query. For example,
when a subset of samples are specified, we only retrieve chunks
in arrays such as \texttt{call\_genotype} for those
samples. Chunks in the variants dimension are retrieved as needed,
and we use a multithreaded strategy to fetch and decode variant chunks
while another thread encodes VCF. Generating VCF text at speed
is a challenging problem, and we use a C extension module to convert
a given set of Zarr chunks represented as numpy arrays to VCF.
Based on the \texttt{region\_index} array computed by \texttt{vcf2zarr},
we use PyRanges~\citep{stovner2020pyranges} to perform efficient interval
search queries.

>>>>

Vcztools is implemented in Python and C, and is available for download 
from the Python package index. 
Based on the \texttt{region\_index} array computed by \texttt{vcf2zarr},
we use PyRanges~\citep{stovner2020pyranges} to perform efficient interval
search queries. 
% While support direct support for VCF Zarr in \texttt{bcftools} would be the 
% ideal outcome, implementation in C within \texttt{htslib} would be significant 
% undertaking.

@@
